Inferring Graphics Programs from Images

### 2017-05-09 paper.tex
added figures for parsing of latex quantitative results
added caption
figure on the first page which gives examples of what the system does

\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfig} 
\usepackage{fancyvrb}

@@

@@

>>>>

\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
%\usepackage{subfig} 
\usepackage{fancyvrb}

@@

\newcommand{\exampleImageSize}{2cm}
\begin{figure}[h]
  \begin{minipage}[t]{0.8\linewidth}  
\begin{tabular}{llll}
  \includegraphics[width = \exampleImageSize]{figures/expert-60.png}&
  \includegraphics[width = \exampleImageSize]{figures/expert-5.png}&
    \includegraphics[width = \exampleImageSize]{figures/expert-17.png}&
    \includegraphics[width = \exampleImageSize]{figures/expert-58.png}\\
  \includegraphics[width = \exampleImageSize]{figures/60.png}&
  \includegraphics[width = \exampleImageSize]{figures/5.png}&
    \includegraphics[width = \exampleImageSize]{figures/17.png}&
    \includegraphics[width = \exampleImageSize]{figures/58.png}
\end{tabular}
\subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.2\linewidth}
    \begin{tikzpicture}
      \node(picture) at (0,0) {\includegraphics[width = 2cm]{figures/expert-31.png}};
      \draw[very thick,->] (picture.south)  -- (0,-2);
    \end{tikzpicture}
    \texttt{FOR} $0\leq i\leq 3$:\\
    \texttt{RECTANGLE} $()$\\
    \texttt{FOR} $0\leq j < i$:\\
    \texttt{CIRCLE} $()$\\
    \subcaption{}
  \end{minipage}
  \caption{(a): Model parses hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}
  \end{figure}

@@

\begin{figure}
  \begin{minipage}[t]{15cm}
    \includegraphics[width = 15cm]{figures/editDistance.png}
  \end{minipage}\\
  \begin{minipage}[t]{15cm}
    \includegraphics[width = 15cm]{figures/accuracy.png}
  \end{minipage}\\
  \begin{minipage}[t]{15cm}
    \includegraphics[width = 15cm]{figures/time.png}
  \end{minipage}
  \caption{Using the model to parse latex output. The model is trained on diagrams with up to 8 objects. As shown above it generalizes to scenes with many more objects. Neither the stochastic search nor the neural network are sufficient on their own.}
  \end{figure}
